README

### 2022-09-29 rmd/supporting_info.Rmd
rmd

knitr::kable(df_sp_list,
             format = "markdown",
             caption = "Fish species found in the study watersheds. Trait information is based on the literature [@gotoEcologicalMorphologicalDivergence1975;@gotoLifeHistoryDistibution1981;@ministryofenvironmentofjapanThreatenedWildlifeJapan2014;@natsumedaEvaluationEcologicalFeatures2010;@fishbaseFishBaseHttpsWww] and expert knowledge. Body size is categoraized as follows: total length (TL) $< 100$ mm (small), $100\\le$  TL $\\le 200$ (medium), and TL $> 200$ (large).")
```

@@

source(here::here("code/figure_theory_2sp.R"))
print(list_g_c[[2]])
```

@@

<!--# Figure S2-S9 -->

>>>>

knitr::kable(df_sp_list,
             format = "markdown",
             caption = "Fish species found in the study watersheds. Trait information is based on the literature [@gotoEcologicalMorphologicalDivergence1975;@gotoLifeHistoryDistibution1981;@ministryofenvironmentofjapanThreatenedWildlifeJapan2014;@natsumedaEvaluationEcologicalFeatures2010;@fishbaseFishBaseHttpsWww] and expert knowledge. Body size is coded as follows: maximum total length (TL) $< 100$ mm (S), $100\\le$  TL $\\le 200$ (M), and TL $> 200$ (L).")
```

@@

source(here::here("code/figure_theory_2sp.R"))
knitr::include_graphics(here::here("output/figure_2sp_model_strong.pdf"))
```

@@

<!--# Figure for the whole community simulation -->
